---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# demspaces

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/andybega/demspaces.svg?branch=master)](https://travis-ci.com/andybega/demspaces)
[![Codecov test coverage](https://codecov.io/gh/andybega/demspaces/branch/master/graph/badge.svg)](https://codecov.io/gh/andybega/demspaces?branch=master)
<!-- badges: end -->

demspaces contains helper functions for the Democratic Spaces Barometer project; see [andybega/democratic-spaces](https://github.com/andybega/democratic-spaces).

*(Note to self: the private dev repo is at andybega/closing-spaces)*

## Installation

Since this package is specific to the democratic spaces project, it will not end up on CRAN. Install from [GitHub](https://github.com/) instead, with:

``` r
# install.packages("remotes")
remotes::install_github("andybega/demspaces")
```

## Example

```{r}
library("demspaces")

data("states")

mdl   <- ds_logistic_reg("v2x_veracc_osp", states)
preds <- predict(mdl, new_data = states)
head(preds)
```

## Meta

There is a Makefile to help with stuff. E.g. to open that static docs:

```bash
make opendocs
```

To add new models, see the `add_new_model.R` script. It will use a template to setup the R and test files. 

